---
title: "Network Analysis"
author: "Hai-Dong  Li"
date: "2018-6-1"
output: html_document
---

# 1. Load packages 
```{r load pkg} 
load_and_install <- function(x) {
    if(!require(x, character.only = TRUE)) {
        install.packages(x)
        library(x, character.only = TRUE)
    }
} # This function from Poislot et al 2017

# All packages

load_and_install("bipartite")
load_and_install("dplyr")
load_and_install("vegan")
load_and_install("igraph")
library(printr)

```

# 2. Inputing data    
This dataset (Schleuning et al. 2011) recorded fruit removal from 33 plant species in different forest strata (canopy,midstory, understory) and habitats (primary and secondary forest) with a standardized sampling design (88 frugivore species, 3447 interactions in 924 observation hours).   

```{r input data}
setwd("C:/Dataset/LearningR/Seminar_BioStat/Network") 
netdata <- read.csv("DispersalNet.csv",row.names = 1)
str(netdata)

```

# 3. Ploting the network
```{r plot web}
op <- par(xpd = T) #allow plotting outside the plot
plotweb(netdata) # bipartite network
par(op)

visweb(netdata,circles = T)

ig<-graph_from_incidence_matrix(netdata, weighted = TRUE)
ig
vertex_attr(ig)$color<-rep("#FF9C0B", length(V(ig)))
vertex_attr(ig)$color[grep(pattern = "FALSE", vertex_attr(ig)$type)]<-"#1C912C"
vertex_attr(ig)$color 

l<-layout_with_dh(ig)
plot(ig, vertex.color=vertex_attr(ig)$cor,vertex.label=NA,
     vertex.size=0.3*igraph::degree(ig),
     edge.width=3*(edge_attr(ig)$weight)/500, 
     edge.color="grey50", 
     edge.curved=0.3,
     layout=l)

```

# 4. Network metrices
      

```{r networklevel}
net_level <- as.data.frame(networklevel(Safariland, index="ALLBUTDD"))
colnames(net_level) <- c("Value")
net_level

```

## 4.1 Specialization  
```{r}
H2fun(netdata) # network level
grouplevel(netdata,index = "generality")

```


## 4.2 Nestedness  
```{r}
Nest_ob <- nested(netdata,method = "NODF2")
nulls <- nullmodel(netdata, N=100, method="r2d")
nested.nulls <- sapply(nulls, function(x) nested (x, method = "NODF2"))

zscore_nest <- (Nest_ob-mean(nested.nulls))/sd(nested.nulls)
zscore_nest

plot(density(nested.nulls), xlim=c(min(Nest_ob, min(nested.nulls)), max(Nest_ob, max(nested.nulls))), 
		main="comparison of observed with null model Patefield")
	abline(v=Nest_ob, col="red", lwd=2)    
	
praw <- sum(nested.nulls>Nest_ob) / length(nested.nulls)
ifelse(praw > 0.5, 1-praw, praw) #  get P-value

```

## 4.3 Modularity  

```{r}
M <- computeModules(netdata)
Q <- M@likelihood
Q
plotModuleWeb(M, displayAlabels = T)
```


# 5. Species level  

```{r degree}
specieslevel(netdata, index="ALLBUTD")
degreedistr(netdata)  
```

```{r specilaization}
dfun(netdata) # gives d-values for the lower trophic level
dfun(t(netdata)) #gives d-values for the higher trophic level

```


# Reference

[1] Dormann, C.F., Fruend, J., Bluethgen, N. & Gruber B. 2009. Indices, graphs and null models:analyzing bipartite ecological networks. The Open Ecology Journal, 2, 7-24.

[2] Dormann, C.F., Gruber B. & Fruend, J. (2008). Introducing the bipartite Package: AnalysingEcological Networks. R news Vol 8/2, 8 - 11.  

[3] Dormann, C.F. (2011). How to be a specialist? Quantifying specialisation in pollination networks. Network Biology 1, 1 - 20.   

[4] Blüthgen, N., Menzel, F. and Blüthgen, N. (2006) Measuring specialization in species interaction networks. BMC Ecology 6, 12  
[5] Schleuning, M., N. Blüthgen, M. Flörchinger, J. Braun, H. M. Schaefer, and K. Böhning-Gaese. (2011) Specialization and interaction strength in a tropical plant–frugivore network differ among forest strata. Ecology 92:26-36.  




